---
title: "BA_Assignment 2"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
  html_notebook: default
---



```{r}
library(tidyverse)
```


```{r}
getwd()
setwd("/Users/thupiliabhinav/Desktop/BA/BA_Assignement 2")
assign_1 <- read.csv("Online_Retail.csv")

```
#1.Breakdown of the number of transactions by countries. Transactions in percentages. Only 1% of transactions.
```{r}
ans1<- group_by(assign_1, Country)%>% count(Country) 
ans1
ans12<- ans1$n*100/sum(ans1$n)
ans12

ans123<-subset(ans12, ans12>1) 
ans123
```
#2.New variable "TransactionValue" and binding to the original dataframe.
```{r}
TransactionValue<- assign_1$Quantity*assign_1$UnitPrice
b_ans1<-cbind(assign_1,TransactionValue)
head(b_ans1)
```
#3.Breakdown of transaction values by countries. Total transaction exceeding 130,000 British Pound.

```{r}
c_ans1<- summarise(group_by(b_ans1,Country), total.value= sum(TransactionValue))
c_ans12 <- filter(c_ans1, total.value>130000)
c_ans12
```
#4.Converting ‘InvoiceDate’ into a POSIXlt object.

```{r}
Temp=strptime(b_ans1$InvoiceDate,format='%m/%d/%Y %H:%M',tz='GMT')
head(Temp)
```

#4.i. Day of the week and hour components dataframe with names as New_Invoice_Date, Invoice_Day_Week and New_Invoice_Hour:
```{r}
b_ans1$New_Invoice_Date <- as.Date(Temp)
```

$4.ii.Date objects
```{r}
b_ans1$New_Invoice_Date[20000]- b_ans1$New_Invoice_Date[10]
```
#4.iii.Convert dates to days of the week
```{r}
b_ans1$Invoice_Day_Week= weekdays(b_ans1$New_Invoice_Date)
```

#4.iv.Convert into a normal numerical value
```{r}
b_ans1$New_Invoice_Hour = as.numeric(format(Temp, "%H"))
```

#4.v.Month as a separate numeric variable
```{r}
b_ans1$New_Invoice_Month = as.numeric(format(Temp, "%m"))
```

#4.a.Percentage of transactions (by numbers) by days of the week
```{r}
n_transactions<- group_by(b_ans1, Invoice_Day_Week) %>% summarise(value=n()) %>% mutate(percentage=value/nrow(b_ans1)*100)
n_transactions
```

#4.b.Percentage of transactions (by transaction volume) by days of the week
```{r}
n_transactions1 <- group_by(b_ans1, Invoice_Day_Week) %>% summarise(value= sum(TransactionValue)) %>% mutate(total= value/sum(value)*100)
n_transactions1
``` 

#4.c.Percentage of transactions (by transaction volume) by month of the year
```{r}
n_transactions2 <- group_by(b_ans1, New_Invoice_Month) %>% summarise(value= sum(TransactionValue)) %>% mutate(total= value/sum(value)*100)
n_transactions2
```

#4.d.The date with the highest number of transactions from Australia?
```{r}
n_transactions3<- group_by(b_ans1, Country) %>% filter(Country=="Australia") %>% group_by(New_Invoice_Date) %>% summarise(value= n()) %>% arrange(desc(value))
n_transactions3
```

#5
```{r}
germany_values<- subset(b_ans1$TransactionValue, b_ans1$Country == 'Germany')
hist(germany_values)
```

#6.Customer had the highest number of transactions. Most valuable customer.
```{r}

f_1 <-group_by(b_ans1,CustomerID) %>% select('CustomerID') %>%  na.omit(b_ans1) %>% summarise(value = n()) %>% arrange(desc(value))
f_1[which.max(f_1$value),]

#Customer-ID 17841 has the highest number of transactions 

f_ans<- summarise(group_by(b_ans1,CustomerID), Value= sum(TransactionValue)) %>% na.omit(b_ans1) 
f_ans[which.max(f_ans$Value),]

#The most valuable customer is Customer-ID-14646.
```

#7. Percentage of missing values for each variable in the dataset
```{r}
missing_val<- colMeans(is.na(b_ans1)*100)
missing_val
```

#8.Number of transactions with missing CustomerID records by countries?
```{r}
missing_transaction <- b_ans1 %>% filter(is.na(CustomerID)) %>% group_by(Country)
summary(missing_transaction$Country)
```


#10.What is the return rate for the French customers?
```{r}
returns <- filter(b_ans1,Country=="France", Quantity<0) %>% count()
total_value<- filter(b_ans1, Country=="France") %>% count()

percentage_returns<- returns/total_value*100
percentage_returns
```

#11.Product that has generated the highest revenue for the retailer
```{r}
revenue<-b_ans1 %>% select(StockCode,TransactionValue) %>% group_by(StockCode) %>% summarise(sum= sum(TransactionValue)) %>% arrange(desc(sum))
revenue

#DOT has the highest revenue generated with sum of 206245.48
```

#12.unique customers are represented in the dataset
```{r}
unique_customer<- b_ans1%>% select(CustomerID) %>% unique() %>% count()
unique_customer
```

