---
title: "Assignment.3-Regression"
output:
  word_document: default
  html_notebook: default
---

```{r}
library(tidyverse)
library(mlbench)
library(tinytex)
```


#1. Create two variables X and Y
```{r}
set.seed(2017)
X=runif(100)*10
Y=X*4+3.45
Y=rnorm(100)*0.29*Y+Y
```

#1.a)Based on the plot do you think we can fit a linear model to explain Y based on X?
```{r}
plot(Y~X)
```
#From above plot we can observe, the relationship between X and Y shows linear regression pattern. As X increases, Y also increases which states X and Y variables have a positive relationship.

#1.b)Simple linear model of Y based on X
```{r}
Model=lm(Y ~X)

summary(Model)
```
#What is the accuracy of this model?
#According above summary, accuracy of model can be derived from R-squared value. R-squared value of above summary is 0.6517. Therefore the accuracy of model is 65.17%.

#Write the equation that explains Y based on X?
#Y=3.6108*X+4.4655

#1.c)How the Coefficient of Determination, R2, of the model above is related to the correlation coefficient of X and Y?
```{r}
cor(X,Y)^2
```


#2. Using mtcars dataset
```{r}
head(mtcars)
```
#2.a) Building a model based on James assumption
```{r}
james_model <- lm(hp~wt, data = mtcars)
summary(james_model)
```
#2.a)Building a model based on Chris assumption
```{r}
chris_model <- lm(hp~mpg, data = mtcars)
summary(chris_model)
```
#Is james assumption better or chris is better?
#From above we can observe, as per James assumption the model shows accuracy of 43.39% and as per Chris assumption the model shows accuracy of 60.24%. We can conclude that Chris assumption of comparing Horse power to mpg is better.

#2.b) what is the estimated Horse Power of a car with 4 cyl and mpg of 22?
```{r}
calc_model <- lm(hp~mpg+cyl, data = mtcars)
summary(calc_model)

predict_model <- predict(calc_model, data.frame(cyl=c(4), mpg=c(22)))
predict_model
```
#The estimated Horse power of a car for 4 cyl and 22 mpg is 88.93618.


#3.Viewing data from mlbench library for current question
```{r}
data("BostonHousing")
str(BostonHousing)
```
#3.a) Build a model to estimate the median value of owner-occupied homes (medv)based on thefollowing variables: crime crate (crim), proportion of residential land zoned for lots over 25,000 sq.ft (zn), the local pupil-teacher ratio (ptratio) and weather the whether the tract bounds Chas River(chas). 
```{r}
boston_model<- lm(medv~crim+zn+ptratio+chas, data = BostonHousing)
summary(boston_model)

```
#Is this an accurate model? - Based on R-squared which is 0.3599 i.e., The accuracy of model is 35%. The model is not accurate enough.

#3.b).i)Imagine two houses that are identical in all aspects but one bounds the Chas Riverand the other does not. Which one is more expensive and by how much? 

#->Factors of Chas is in factors of 1 and 0. Identical houses is 1 and who dont have identical houses have 0. And Estimate Std. of chas1 in relation to medv is 4.58393. 

#Medv = 49.91868 + (-0.26018) + 0.07073 + (-1.49367) + 4.58393(1) =   52.81949.

#Medv = 49.91868 + (-0.26018) + 0.07073 + (-1.49367) + 4.58393(0) =  48.23556.

#Comparing from above, Identical houses for chas River for which factor is 1, the value as per estimated std 52.81949. When factor is 0 the value as per estimated std. is 48.23556. By comparison of factors 1 and 0, chas River is expensive by 4.58393  for factor 1 in $1000.

#3.b.ii)Imagine two houses that are identical in all aspects but in the neighborhood of one of them the pupil-teacher ratio is 15 and in the other one is 18. Which one is more expensive and by how much?

#Medv = 49.91868 + (-0.26018) + 0.07073 + (-1.49367)(15) + 4.58393= 31.9081.

#Medv = 49.91868 + (-0.26018) + 0.07073 + (-1.49367)(18) + 4.58393= 27.4271.

#Difference between Pupil-teacher ratio for 15 and 18 is 4.48101.Therefore, Pupil-teacher ratio for 15 is expensive by 4.48101 when compared to pupil-teacher ratio of 18.

#3.c)Which of the variables are statistically important?
#when comparing dependent and independent variables to show statistical importance, we would like to see p values being as small as possible.From above, p values of crim, zn, ptratio,chas when compared to medv are lowest. We can conclude that all the values are statistically significant.

#3.d)Anova analysis and determine the order of importance of these four variables.?
```{r}
anova_model <- anova(boston_model)
anova_model
```

#In Annova analysis, the importance of variables is defined by the sum squared values. From above the values of sum squared, in order of importance are as follows: crim,zn,ptratio,chas.

